sensi_an_rotations1. Start of sensitivity analysis for rotations.

### 2019-02-13 inst/documents/rotations_notes.Rmd
comments
starting mortality calculations

@@

# Jim suggest

>>>>

13/2/2019

looking at saving tested mortality levels for the different insecticides over time
(as a prelude to using it as a criteria for switching insecticides)

resistance frequency results are saved in df_results
think I can create df_mort with the same structure and then put it through the same plotting function.

but df_results summaries are only calculated at the end so df_mortali couldn't allow mortality to be used as a switching criteria.

BUT also I need an equivalent of RAF[] (without the sex dimension, or maybe easier to leave it in)
to enable switching

  # RAF[, 'm', 'intervention', 1] = freqs
  # dim1 :n_insecticides
  # dim2 :sex: m,f
  # dim3 :site: intervention,refuge
  # dim4 : generations

see run_rot for initial test mortality calculation

@@

# Jim suggests making flow chart
# make branch of rotations repo and send instructions to Jim
# get rotations repo back from Ian
